---
title: "Power Curve Hw"
author: "Alison Pedraza"
date: "2/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


We want to make the probability of making a Type I and Type II error very small with different values of effectiveness (p = 0.6 to  p = 0.8).

We can do this by increasing the Power (the probability of rejecting the null hypothesis when it is false) and so increasing alpha.

We also want to find out the critica value for this experiment given the different values of effectiveness. 


#### Power Plot with significance level 0.95 - a realy big Power

If 60% of the people show that the aspirine is effective, how many people would we need to make sure we don't make a Type I error? : we reject the null hypothesis when we should not.


  - With significance level = 0.95 and p = 0.6
  - The critical value = .68 

With 60% effectiveness, the value of m (number of people) you would need to be cured to make the probability of a Type I error small is 68.

  - m = 68


```{r echo=FALSE}

n = 100
p = 0.6
sd = sqrt((p * (1 - p)/n))


critical_value_1<-qnorm(0.95,p,sd)
critical_value_1

p_hat_seq = seq(0.4, 1, 0.01)
power<-1-pnorm(critical_value_1,p_hat_seq,sd)
plot(p_hat_seq, power, type = "l", ylab = "Power" , col = "red")

abline(h = 0.05, col = "grey", lwd = 1)
abline(h = 0.95, col = "grey", lwd = 1)
abline(v = 0.6, col = "grey", lwd = 1)
abline(v = 0.8, col = "grey", lwd = 1)

```


<br>

#### Power Plot with significance level 0.05

If 80% of the people show that the aspirine is effective, how many people would we need to make sure we don't make a Type II error? : we reject the null hypothesis when we should not.

Type II error = 1 - alpha 

  - With signigicance level of 0.05 and p = 0.8
  - critical value = .73
  
If we assign the aspirine to 100 people with p = 0.8, at least 73 people would need to be cured.

  - m = 73
  
  <br>
  
```{r echo = FALSE}

n = 100
p = 0.8
sd = sqrt((p * (1 - p)/n))

## critical value
critical_value_2<-qnorm(0.05,p,sd)
critical_value_2

p_hat_seq = seq(0.4, 1, 0.01)
power<-1-pnorm(critical_value_2,p_hat_seq,sd)

plot(p_hat_seq, power, type = "l", ylab = "Power" , col = "blue")
abline(h = 0.05, col = "grey", lwd = 1)
abline(h = 0.95, col = "grey", lwd = 1)
abline(v = 0.6, col = "grey", lwd = 1)
abline(v = 0.8, col = "grey", lwd = 1)

```


